Weather vanes and runaways: Bow shocks across the HR diagram

### 2017-10-13 papers/Paper1/obs-bowshocks.tex
Split observational material into its own paper !!!!!!!

\title[Bowshock shapes]{True versus apparent shapes of astrophysical bow shocks}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Tarango Yong \& Henney]{
  Jorge A. Tarango Yong \& William J. Henney\\
  \AddressCRyA
}
\begin{document}
\maketitle
\begin{abstract}
  Stellar bow shocks are the result of the supersonic interaction
  between a stellar wind and its environment.  Some of these are
  "runaways": high-velocity stars that have been ejected from a star
  cluster.  Others are "weather vanes", where it is the local
  interstellar medium itself that is moving, perhaps as the result of
  a champagne flow of ionized gas from a nearby \hii{} region.  We
  present a new two-dimensional classification scheme for the shape of
  such bow shocks, which accounts for both the apex (pointy versus
  flat) and the wings (open versus closed).  For different theoretical
  bow shock models, we show how variations in the true shape can be
  disentangled from projection effects due to variations in the
  inclination angle.  We apply our classification scheme to three
  different observational datasets: mid-infrared arcs around hot
  main-sequence stars (\(N = 227\)), far-infrared arcs around luminous
  cool stars (\(N = 7\)), and emission-line arcs around proplyds and other
  young stars in the Orion Nebula (\(N = 18\)).  We find significant
  differences between the three datasets: cool star bow shocks have
  markedly more closed wings than hot star bow shocks, while
  differences in the shape of the apex region are only marginally
  significant.  The Orion Nebula arcs, on the other hand, have both
  significantly more open wings and significantly flatter apices than
  the hot star bow shocks.  We discuss the implications of these
  differences for understanding the physics of the bow shock
  interaction in the three classes of sources.
\end{abstract}

\input{sec-intro}
\input{sec-generic-model}
\input{sec-projection}
\input{sec-conic}
\input{sec-thin-shell}
\clearpage
\input{sec-quadrics-observations}
\input{sec-conclusions}
\clearpage
\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}
\appendix
\input{app-parabola}
\input{app-rcurv}
\input{app-r90}
\input{app-wilkinoid}
\input{app-dust-wave}
\input{app-p-values}

>>>>

\title[Stellar bow shocks]{Weather vanes and runaways: Bow
  shocks across the HR diagram}

\newcommand\AddressCRyA{Instituto de Radioastronom\'{\i}a y Astrof\'{\i}sica,
  Universidad Nacional Aut\'onoma de M\'exico, Apartado Postal 3-72,
  58090 Morelia, Michoac\'an, M\'exico}
\author[Henney \& Tarango Yong]{
  William J. Henney \& Jorge A. Tarango Yong \\
  \AddressCRyA
}
\begin{document}
\maketitle
\begin{abstract}
  Stellar bow shocks are the result of the supersonic interaction
  between a stellar wind and its environment.  Some of these are
  "runaways": high-velocity stars that have been ejected from a star
  cluster.  Others are "weather vanes", where it is the local
  interstellar medium itself that is moving, perhaps as the result of
  a champagne flow of ionized gas from a nearby \hii{} region.
  We recently proposed a new two-dimensional classification scheme for
  the shape of such bow shocks, which we here apply to three very
  different observational datasets.  These are: (1)~mid-infrared arcs
  around hot main-sequence stars (\(N = 227\)); (2)~far-infrared arcs
  around luminous cool stars (\(N = 7\)); and (3)~emission-line arcs
  around proplyds and other young stars in the Orion Nebula
  (\(N = 18\)).  We find significant differences between the three
  datasets: cool star bow shocks have markedly more closed wings than
  hot star bow shocks, while differences in the shape of the apex
  region are only marginally significant.  The Orion Nebula arcs, on
  the other hand, have both significantly more open wings and
  significantly flatter apices than the hot star bow shocks.  We
  discuss the implications of these differences for understanding the
  physics of the bow shock interaction in the three classes of
  sources.
\end{abstract}

\input{sec-obs-intro}
\clearpage
\input{sec-quadrics-observations}
\input{sec-obs-conclusions}
\clearpage
\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}
\appendix
\input{app-p-values}

### 2017-10-13 papers/Paper1/sec-obs-conclusions.tex
Split observational material into its own paper !!!!!!!

\section{Conclusions}
\label{sec:conc}

%\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}

We developed a method to estimate the shape of a generic bow shock product of the
interaction of two winds as well as it apparent shape due to it orientation relative to the line of sight, asuuming
the bow shock is geometrically and optically thin.

In the general case we require numerical techniques, but is possible to handle analytically the apparent shape of
the quadrics of revolution.

Also we made a generalization of \CRW{} work where the weakest interacing wind is hemispherical and anisotropic where its
density follows a power law of $\cos\theta$. Although other models also may be used.

In any case we developed a form to derive a set of measurable radii which are used as comparison between the \CRW{} model, the quadrics
of revolution and further observations. Our goal is to apply this work to the bow shock shapes observed in the core of the Orion Nebula Cloud
(ONC) due to the interaction of the photoevaporated wind from proplyds and the stellar wind of \thC{}.

%and was applied to the proplyds in the core of the ONC.
%We started measuring the projected characteristic radii $(R'_0,R'_c)$ for each proplyd in our
%sample and compare them with the ``conic equivalent'' of a two winds interaction model based 
%on \CRW{} work to estimate the intrinsic bow shock shape and get the ionizing flux for ionization balance 
%and the stagnation pressure for our sample of proplyds.
%Most results are consistent with a proplyd's photoevaporated flow with an anisotropic density
%distribution, with different anisotropy degrees. We ound that LV4 has the least anisotropic flow,
%while LV2 has the most anisotropic flow. And for the 177-341, 169-348 and 180-331 we found out that 
%the stellar wind is not enough to keep their bow socks stationary.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quadrics-bowshock"
%%% End:

>>>>

\section{Conclusions}
\label{sec:conclusion}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "obs-bowshocks"
%%% End:
